|

### 2023-05-01 paper/01-introduction.Rmd
Some edits.

Pro football focus (PFF) defines pass-rush productivity as: 
$$
\frac{\frac{(\# Hurries + \# Hits)}{2} + \# Sacks}{\#PassRush Snaps}
$$.

@@

(https://www.pff.com/news/pro-pff-signature-statistics-a-glossary#:~:text=Time%20in%20Pocket,time%20until%20a%20quarterback%20scrambles)

>>>>

Pro football focus (PFF) defines pass-rush productivity as: 
$$
\frac{\frac{1}{2}(\# Hurries + \# Hits) + \# Sacks}{\#PassRush Snaps}
$$.

@@

<!-- (https://www.pff.com/news/pro-pff-signature-statistics-a-glossary#:~:text=Time%20in%20Pocket,time%20until%20a%20quarterback%20scrambles) -->

<!-- (https://www.espn.com/nfl/story/_/id/34536376/2022-nfl-pass-rushing-run-stopping-blocking-leaderboard-win-rate-rankings-top-players-teams) -->

### 2023-05-01 paper/02-data.Rmd
Some edits.

# Data {#sec:data}

We use the tracking data made available in the 2023 NFL BDB competition for our investigation. The data corresponds to 8557 passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. The aforementioned NGS data provides the on-field location, speed, direction, and orientation of each player on the field (and the ball) at a rate of 10 Hz, along with event annotations (e.g., ball snapped, pass thrown, etc.). In this particular dataset, there are _INSERT NUMBER_ unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked. (_VERIFY THIS STATEMENT MAKES SENSE_)

>>>>

# Data {#sec:data}
```{r eval = FALSE, echo = FALSE}
pass_rush <- read_csv(here("data", "pass_rush.csv.gz"))
pass_rush %>% select(gameId, playId, frameId) %>% n_distinct()
```

We use the tracking data made available in the 2023 NFL BDB competition for our investigation. The data corresponds to 8557 passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. The aforementioned NGS data provides the on-field location, speed, direction, and orientation of each player on the field (and the ball) at a rate of 10 Hz, along with event annotations (e.g., ball snapped, pass thrown, etc.). In this particular dataset, there are _INSERT NUMBER_ (our cleaned dataset has 251060 unique frames) unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked. (_VERIFY THIS STATEMENT MAKES SENSE_)
